Modelling the City of Melbourne Pedestrian Data

### 2017-05-07 presentation/proposal_pres.Rmd
changed research plan to numbering

- Imputation that incorporates time and space
- Creating a predictive model for each sensor
- Investigation of visual methods for space-time counts
- Development of a Shiny app: interface design, computation and data backend
- Generation of a dynamic spatial model (if time permits)

>>>>

1. Imputation that incorporates time and space
2. Creating a predictive model for each sensor
3. Investigation of visual methods for space-time counts
4. Development of a Shiny app: interface design, computation and data backend
5. Generation of a dynamic spatial model (if time permits)
